---
title: "Cuisine Score by Alcohol Consumption"
author: "Mustafa Telab"
date: "10/25/2020"
output:
  ioslides_presentation:
    self_contained: true
    widescreen: true
    smaller: true
    autosize: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(RCurl)
```

## Cuisine Score by Alcohol Consumption

A survey was conducted by the FiveThirtyEight to uncover how the cultural cuisines rank among American taste.  1373 Americans were polled to assign ordinal ranking to 32 countries.

```{r}
getfile_1 <- getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/alcohol-consumption/drinks.csv") 
alcohol <- read.csv(text = getfile_1)
```

A separate data set was collected by the World Health Organization cataloging the annual alcohol consumption of nations across the globe.
```{r}
getfile_2 <- getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/food-world-cup/food-world-cup-data.csv") 
food <- read.csv(text = getfile_2, header=FALSE, stringsAsFactors=FALSE, na.strings = c("N/A",""))
```

We will test the correlation between these data sets to answer wether or not the alcohol consumption of a nation is an indicator of how appealing their cuisine is to Americans.  Then we can attempt to predict the cuisine scores for the nations that do not appear on the 32 country survey.

## Data Cleaning

Header configuration is not importing correctly for the food data set.  As a workaround, the data is imported without headers, and the appropriate naming is extracted from the first row.

```{r}
headers <- food[1,]
headers_new <- str_replace(str_extract(headers, "(([:upper:])[:lower:]+[:punct:]?)$"), "[:punct:]", "")
food <- slice(food,-1)
colnames(food) <- headers_new
colnames(food)[1:3] <- c("respondant_id", "international_cuisine_knowledge", "international_cuisine_interest")
```

## Data Manipulation
Pivot
```{r}
food_pivot <- food %>%
  pivot_longer(cols = Algeria:Ireland, names_to = "country", values_to = "rating", values_drop_na = TRUE)%>%
  mutate(rating = as.numeric(rating))
```
Aggregate
```{r}
food_rating_agg <- food_pivot %>%
  group_by(country)%>%
  summarise(avg_rating = mean(rating))
```
Now we can join the tables for comparison
```{r}
food_drink <- food_rating_agg%>%
  inner_join(alcohol)
```

## Cuisine Score by Total Alcohol Consumption 
```{r, echo = FALSE}
food_drink %>%
ggplot(aes(x=total_litres_of_pure_alcohol, y = avg_rating))+ 
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)+
  ggtitle("Cuisine Score by Total Per Capita Alcohol Consumption")+
  xlab("Country Per Capita Alcohol Consumption(liters)")+
  ylab("Cuisine Score")
```


## Correlation
```{r}
food_drink %>% summarise(cor(total_litres_of_pure_alcohol,avg_rating))
```
## Summary
With the below p-value, the results are not significant enough to reject the null hypothesis that the correlation is 0.  
```{r}
summary(lm(food_drink$total_litres_of_pure_alcohol ~ food_drink$avg_rating))
```

## Multiple Regression
The WHO data has additional parameters broken out by alcohol type that we can also test.
```{r}
summary(lm(food_drink$avg_rating ~ food_drink$spirit_servings +food_drink$beer_servings +food_drink$wine_servings))
```



```{r}
panel.hist <- function(x, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(usr[1:2], 0, 1.5) )
    h <- hist(x, plot = FALSE)
    breaks <- h$breaks; nB <- length(breaks)
    y <- h$counts; y <- y/max(y)
    rect(breaks[-nB], 0, breaks[-1], y, col = "cyan", ...)
}
```

```{r}
panel.cor <- function(x, y, digits = 2, prefix = "", cex.cor, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    r <- abs(cor(x, y))
    txt <- format(c(r, 0.123456789), digits = digits)[1]
    txt <- paste0(prefix, txt)
    if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
    text(.5, .5, txt, cex = cex.cor * r)
}
```

## Comparing Variables
```{r}
pairs(food_drink[2:5], panel = panel.smooth,lower.panel = panel.cor, 
      cex = 1.5, pch = 1, bg = "light blue", horOdd=TRUE,
      diag.panel = panel.hist, cex.labels = 1, font.labels = 3)
```



## Multiple Regression Results

The Spirit Servings variable is doing the heavy lifting, so we move forward without the remaining variables as they are not contributing.

```{r}
summary(lm(food_drink$avg_rating ~ food_drink$spirit_servings))
```


## Cuisine Score by Spirit Consumption 
```{r, echo = FALSE}
food_drink %>%
ggplot(aes(x=spirit_servings, y = avg_rating))+ 
  geom_point()+
  geom_smooth(method = "lm", se = FALSE)+
  ggtitle("Cuisine Score by Spirit Consumption")+
  xlab("Country Per Capita Spirit Servings")+
  ylab("Cuisine Score")
```
## {.flexbox .vcenter}
```{r}
cor.test(food_drink$avg_rating, food_drink$spirit_servings)
```

# Conditions
##  {.flexbox .vcenter}
```{r, echo = FALSE}
scorespirit_lm <- lm(avg_rating ~ spirit_servings, data = food_drink)
scorespirit_res <- resid(scorespirit_lm)

food_drink %>%
ggplot(aes(x= spirit_servings, y = scorespirit_res))+
  geom_point()+
  xlab("Fitted Values")+
  ylab("Residuals")+
  ggtitle("Fitted vs Residual")+
  geom_abline(aes(slope = 0,intercept = 0))
```

##  {.flexbox .vcenter}
```{r, echo = FALSE}
qqnorm(scorespirit_res)
qqline(scorespirit_res)
```

##  {.flexbox .vcenter}
```{r, echo = FALSE}
food_drink%>%
  ggplot(aes(x=scorespirit_res))+
  geom_histogram()+
  ggtitle("Residual Histogram")

```

## Conclusion

- Data Set of Cuisine Ranking is small, just barely above what may be considered appropriate(>30).
- Only significant variable is spirit serving but the data is heavily skewed.
- Residual variability is not evenly distributed, and normality is questionable.

**Although the results are interesting and some of the statistics are tempting to trust, I believe we cannot make reasonable predictions of how Americans would rate various ethic cuisines base of the country of origins propensity towards alcohol.**